---
title: "workout01-nick-schoettle.Rmd"
author: "Nick Schoettle"
date: "10/4/2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##1. File Structure

cd /Users/Nick/desktop/hw-stat133-NickSchoettle

mkdir workout1/

touch README.md

mkdir data/

mkdir code/

mkdir output/

mkdir report/

##2. Create a README.md File

git init 

git add README.md

git status

git commit -m "committing readme file"

rm -rf .git

git remote set-url origin https://github.com/stat133-f18/hw-stat133-NickSchoettle.git

git remote -v

git add README.md

git status

git commit

git push --set-upstream origin master


https://github.com/stat133-f18/hw-stat133-nickschoettle
https://github.com/stat133-f18/hw-sta
https://github.com/stat133-f18/hw-sta


##3. Create a Data Dictionary 

All work included in nba2018-dictionary.md file inside data folder

##4. Data Preparation

All work included in make-teams-table.R file inside code folder

##5. Ranking of Teams

```{r, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)

library(readr)

library(dplyr)

library(ggplot2)

teams <- read_csv("/Users/Nick/desktop/hw-stat133-NickSchoettle/workout01/data/nba2018-teams.csv")

ggplot(teams, aes(x=reorder(team, teams$salary), y= teams$salary)) + geom_bar(stat='identity') + coord_flip() + labs(y = "Salary (in millions)", x = "Team", title = "NBA Teams ranked by Total Salary") + geom_hline(yintercept = mean(teams$salary), colour = "red")

ggplot(teams, aes(x=reorder(team, teams$points), y= teams$points)) + geom_bar(stat='identity') + coord_flip() + labs(y = "Total Points", x = "Team", title = "NBA Teams ranked by Total Total Points") + geom_hline(yintercept = mean(teams$points), colour = "red")

ggplot(teams, aes(x=reorder(team, teams$efficiency), y= teams$efficiency)) + geom_bar(stat='identity') + coord_flip() + labs(y = "Total Efficiency", x = "Team", title = "NBA Teams ranked by Total Efficiency") + geom_hline(yintercept = mean(teams$efficiency), colour = "red")

teams$efficiency_per_dollar <- teams$efficiency/teams$salary

ggplot(teams, aes(x=reorder(team, teams$efficiency_per_dollar), y= teams$efficiency_per_dollar)) + geom_bar(stat='identity') + coord_flip() + labs(y = "Total Efficiency per Million Dollars", x = "Team", title = "NBA Teams ranked by Total Efficiency per Million Dollars") + geom_hline(yintercept = mean(teams$efficiency_per_dollar), colour = "red")

```

I chose to calculate efficiency per dollar, to look at the return (efficiency performance) per dollar paid to the teams' rosters. This is a good measure of how well a team is spending their money on players that will boost performance (performance measured by efficiency).

##Comments and Reflections

Was this your first time working on a project with such file structure?

- Yes, the file structure seems like a good way to organize different parts to a project, but I feel I need some time to get used to it.

Was this your first time using relative paths?

- Yes, they are important because they let you easily navigate to the other folder/file locations within the master folder of the file. This is helpful because on different users' computers the base of the path will likely be different, but with relative paths, once the path is established into the project folder the relative file paths work properly for all.

Was this your first time using an R script?

- No, just writing code seems simpler, and also gives the ability to comment things out, however, it limits your ability to show different outputs, etc.

What things were hard, even though you saw them in class/lab?

- By far, the hardest part is dealing with adding files to github. I spent hours with my lab instructor and lab assistant trying to solve a problem, but they could never solve it.

What was easy(-ish) even though we haven’t done it in class/lab?

- The coding with base r, dplyr, and ggplot were all very easy.

Did anyone help you completing the assignment? 

- Lab instructor and lab assistant both tried to help me add things to github, but after over an hour of trouble shooting we made no progress together.

How much time did it take to complete this HW?

- 5 hours

What was the most time consuming part?

- Navigating github!!

Was there anything interesting?

- Yes, I find the data manipulating and graphing very intersting and useful.




